\title{Sara and her Trip to the Pet Store (Adventure Story Project)}
\author{Crystal Lin, Nicholas Tating, Stephan Min, Jim Xu}

\documentclass{article}
\usepackage[utf8]{inputenc}
\begin{document}
\LARGE\noindent
\maketitle

\Large
Sara sat at home alone. After an exhausting week at work she lay on her couch watching Netflix and eating Cheetos.As she was stuffing her face full of finger licking goodness, she looked outside her window to see her neighbor, Chris playing ball with his adorable Corgi, Jojo. Jojo hopped back and forth chasing the ball across the green and lush yard. "What as cute pupper.", thought Sara as she walked outside to get a better view of the doggo and its owner enjoying each other's company. As she approached Chris's lawn, Jojo's smile widened and his stubby Corgi tail wagged in happiness as he bumbled over to greet Sara in slobbery kisses and wet licks. In return Sara gave Jojo an enthusiastic belly rub and a couple pats on the head as Jojo's tongue flapped around in enjoyment. Then Sara stood up to talk to Chris. As Sara and Chris discussed their mutual fondness of puppies and pets, Jojo waddles around the lawn runs around the lawn chasing a butterfly that he a seen land on a flower. As a Sara and Chris end their conversation and Sara turns around to head back to her home. Walking home, Sara thought about how great of a companion Jojo was to Chris and right then, at that moment, her mind was set. Sara was going to get a pet to be her loyal friend. But, the question was what type of pet was she going to get? Sara not only loved dogs but she also loved cats. As a child her family had a kitten that Sara loved to play with, and she enjoyed the relaxed personality of cats. As she walked to her car on the way to the pet store, Sara was excited to gain a loyal and lifelong companion.

The next day, Sara went to the local pet store to find her new best friend. She walked through the automatic doors and was greeted by the smell of animals, mostly the smell of dogs as a lot of customers had brought their dogs with them to the store. Sara walked around realizing she had so many options for pets. She could get a parrot and teach it how to talk, but figured it would get old after a while especially since it would repeat the same phrases over and over. She could get a fish, or a bunch of fish. She thought about getting a beta fish since they are colorful and pretty. She thought about getting a guinea pig or a hamster since they are so small and fluffy. She walked down the reptile isle and thought about getting a lizard or a snake. Sara observed them for a few minutes and came to the conclusion that she would be bored of them. The reptiles were calm and not very interactive. After walking around, Sara knew that she needed a companion to interact with. She wanted a companion that she could play with or cuddle with. No bird, fish, or reptile can provide that for her. A hamster? Maybe. But Sara decided against it. A hamster couldn't interact with her the way a cat or a dog would. She started to make her way towards the back of the store where the dogs and cats were on display. A thought crossed her mind that excited her though she knew it was unrealistic. She imagined having exotic and unusual animals as a pet. Leopards, cheetahs, bear cubs, ferrets, raccoons, falcons. Sara chuckled at the idea as she knew it was very difficult if not impossible to have these animals as pets, but it was an entertaining thought. Sara arrived to the back where she was confronted with the dilemma of the day: dog or cat?

Sara decided to get a fluffy doggo and came home with a Pomeranian. She named him Poof. Sara rejoiced as she could now truly appreciate the cute dog videos her friends tagged her in. Just as she'd imagined, the two of them played and cuddled together all day. Over time, Poof learned how to do lots of cool tricks--he could jump, do a flip in midair, and catch a snack in his mouth. Poof could also make any human die of cuteness by rolling around on the floor in a cuddly ball of fur. Chris would bring Jojo over, and the four of them would play frisbee in the backyard while listening to country music and enjoying lemonade. At night, the four of them would dance on the beach and watch the sunset, as the two dogs barked at the seagulls. Sara knew she had made a lifelong friend in Poof. Over time, Poof kept improving his dog tricks, and Sara became better at training her dog. Now, Poof could breakdance and even ice skate, while balancing a beach ball on his nose. He eventually developed into a prodigious piano player, occasionally dabbling in musical composition. With every difficult trick Poof mastered, Sara swelled with pride at watching him grow. She looked after Poof like her son, making sure he exercised every day and ate enough vegetables. At the age of 8, Poof got into Haas and became the first doggo-snake in the school's history. As Poof became more self-sufficient over time, he knew he needed to eventually find a job to support his owner, Sara. After graduating, Poof decided to work at Google. Sara always packed him his favorite lunch, dog biscuits. After hoping to make a lifelong friend at the pet store one day, Sara knew that her wish had come true. Poof was the best doggo she could ask for.
\end{document}
